taxize - taxonomic search and retrieval in R

### 2013-05-29 inst/doc/taxize_withcode_appA.Rnw

\documentclass[letterpaper,superscriptaddress,showkeys,longbibliography,10pt]{revtex4-1}
\usepackage[utf8]{inputenc}
\usepackage{color,dcolumn,graphicx,hyperref}
\usepackage[titletoc, title]{appendix}
\hypersetup
{
colorlinks = true, linkcolor = blue, citecolor = blue, urlcolor = blue,
}

\begin{document}

<<setup, include=FALSE, cache=FALSE>>=
## set global chunk options
opts_chunk$set(fig.path='figure/', fig.align='center', fig.show='hold', par=TRUE, warning=FALSE, message=FALSE, error=FALSE, comment=NA)
@

\begin{appendices}
\section{A complete reproducible workflow, from a species list to a phylogeny, and distribution map.}

@@

<<classification, eval=TRUE, cache=TRUE>>=
# As we already have Taxonomic Serial Numbers from ITIS, let's just get classifications from ITIS. Note that we could use NCBI instead.
class_list <- classification(tsns)
sapply(class_list, nrow)

@@

\begin{figure}[!ht] 
\centering 
<<map, eval=TRUE, dev='pdf', out.width='.8\\textwidth'>>=
library(rgbif)
library(ggplot2)

@@

\end{appendices}
\end{document}

>>>>

\section{A complete reproducible workflow, from a species list to a phylogeny, and distribution map.}

@@

<<classification, eval=TRUE, cache=TRUE>>=
# As we already have Taxonomic Serial Numbers from ITIS, let's just get classifications from ITIS. Note that we could use uBio instead.
class_list <- classification(tsns)
sapply(class_list, nrow)

@@

\begin{figure}[!ht] 
\centering 
<<map, eval=TRUE, dev='pdf', out.width='.8\\textwidth', cache=TRUE>>= 
library(rgbif)
library(ggplot2)

@@
